### 2019-11-12 paper/paper.tex
Adds a config and associated binary to set the competition with a logistic function

The first term on the right describes the spatial gradient (indicated by
$\nabla\vcdot$) of a quantity referred to in models of heat diffusion as the
`flux' (the term enclosed by parentheses). The central idea in heat diffusion
models is that the change in temperature (over time) at a given location is
proportional to the gradient in the temperature (over space) at that
location. Substituting the branching density for heat, axons from a given
thalamic projection are thus assumed to branch laterally across the cortical
sheet at a rate given by the diffusion constant $D$. Lateral branching is
augmented by a measure of the local alignment between the branching density
and the gradient in the concentration of each of $M$ distinct molecular
signals, $\rho(\mb{x})$. The influence of a given signal (indexed by $j$) on a
given thalamic projection (indexed by $i$), is determined by the parameter
$\gamma_{i,j}$. Interactions for which this value is positive encourage axon
branching in the direction in which the concentration of the signal is
increasing, whereas negative interactions encourage branching in the opposite
direction. Hence the axons of a given thalamic projection are assumed to
branch towards either higher or lower concentrations of each signalling
molecule.

@@

There exists an element of competition in the model system specified by
Eqns. \ref{eq:dc} \& \ref{eq:da}. The term $\left(1 -
\sum_{i=1}^{N} c_i(\mb{x}, t)\right)$ in Eq.~\ref{eq:dc} ensures that once the available synaptic
receptors in a region have been fully occupied, say by thalamocortical types
$i=2$ and $i=3$, there is no longer the possibility for type $i=1$ to form any
synapses. This competition turns out to be relatively weak, because it does
not strongly affect the branching density in that region; two or more TC axon
types can be branching equally in the region, leading to roughly equal numbers
of connections being made up until the connection limit is reached.

To introduce an element of competition between the branching of
thalamocortical axon types, we introduced the new term $\chi$ given by
%
\begin{equation} \label{eq:branch_comp}
\chi(\mb{x}, t) = - \frac{\epsilon  a_i}{N-1} \sum_{i' \ne i}^{N} a_{i'}(\mb{x}, t)
\end{equation}
%
which leads to a reduction in the rate of increase of branching density for
axon type $i$ in regions where the branching density of \e{other} axon
types is high.

@@

>>>>

The first term on the right describes the divergence (indicated by
$\nabla\vcdot$) of a quantity referred to in models of heat diffusion as the
`flux' (the term enclosed by parentheses). The central idea in heat diffusion
models is that the change in temperature (over time) at a given location is
proportional to the gradient in the temperature (over space) at that
location. Substituting the branching density for heat, axons from a given
thalamic projection are thus assumed to branch laterally across the cortical
sheet at a rate given by the diffusion constant $D$. Lateral branching is
augmented by a measure of the local alignment between the branching density
and the gradient in the concentration of each of $M$ distinct molecular
signals, $\rho(\mb{x})$. The influence of a given signal (indexed by $j$) on a
given thalamic projection (indexed by $i$), is determined by the parameter
$\gamma_{i,j}$. Interactions for which this value is positive encourage axon
branching in the direction in which the concentration of the signal is
increasing, whereas negative interactions encourage branching in the opposite
direction. Hence the axons of a given thalamic projection are assumed to
branch towards either higher or lower concentrations of each signalling
molecule.

@@

There exists an element of competition in the model system specified
by Eqns. \ref{eq:dc} \& \ref{eq:da}. The term $\left(1 -
\sum_{i=1}^{N} c_i(\mb{x}, t)\right)$ in Eq.~\ref{eq:dc} ensures that
once the available synaptic receptors in a region have been fully
occupied, say by thalamocortical type $i=1$, there is no
longer the possibility for type $i=2$ to form any synapses. This
competition turns out to be relatively weak, because it does not
strongly affect the branching density in that region. In the model, it
is possible for two or more TC axon types to have roughly equal
branching density in some region, leading to roughly equal numbers of
connections for each TC type being made,  up until the `hard' connection
limit is reached.

To introduce competition between the \emph{branching} of thalamocortical axon
types, we introduced the new term $\chi$ given by
%
\begin{equation} \label{eq:branch_comp}
\chi(\mb{x}, t) = - \frac{\epsilon  a_i}{N-1} \sum_{i' \ne i}^{N} a_{i'}(\mb{x}, t)
\end{equation}
%
which leads to a reduction in the rate of increase of branching density for
axon type $i$ in regions where the branching density of \e{other} axon
types is high.

@@

To increase the strength of the competition, we could take the power
of the branching density:
%
\begin{equation} \label{eq:branch_comp_pow}
\chi(\mb{x}, t) = - \frac{\epsilon  a_i}{N-1} \sum_{i' \ne i}^{N} (a_{i'})^l
\end{equation}
%
with $l>1$. This competition term can quickly become excessively
large, so to preserve the geometric shape of the function for small
$a$, whilst representing the idea that the amount of branching
competition has an upper bound, we pass the function through a
logistic function.  This leads to the following branching equation:

%
\begin{equation} \label{eq:branch_comp_pow_logistic}
\chi(\mb{x}, t) = - \frac{\epsilon a_i}{N-1} \sum_{i' \ne i}^{N}
\frac{1}{1 + e^{-m (a_{i'})^l}} - \frac{1}{2}
\end{equation}
%
$\epsilon$ represents the maximum value of the competition term for TC
type $i$. The parameter $m$ controls the steepness of the function.
